%-------------------------
% Katie Ng - Resume
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\usepackage[most]{tcolorbox}


% Set the margins
\geometry{left=1.4cm, top=1.5cm, right=1.4cm, bottom=1.5cm}


% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]


%-------------------------
% Custom commands

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \hspace{-3mm}{#1}:\hspace{1mm} & \hspace*{0pt}\hfill{\footnotesize{ #3}} \vspace{-0.5mm}\\ \hspace{-2.9mm}#2 
    \end{tabular*}
    \vspace{0mm}
}

\newcommand{\resumeExp}[4]{
\vspace{1mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \hspace{-4.4mm} \small\textbf{#1} & {\footnotesize{#3}}\vspace{-0.5mm}\\
        \hspace{-4.3mm} \footnotesize{\text{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-6.1mm}
}

\newcommand{\resumeProject}[4]{
\vspace{1mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \hspace{-4.4mm} \small\textbf{#1} & {\footnotesize{#2}}\vspace{-0.5mm}\\
    \end{tabular*}
    \vspace{-6.5mm}
}

\newcommand{\resumeEdu}[4]{
\vspace{0mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \hspace{-4.3mm} \small\textbf{#1} & \footnotesize{#3}\vspace{-1.2mm} \\
        \hspace{-4.3mm} \footnotesize{#2} & \footnotesize{#4}
    \end{tabular*}
    \vspace{0mm}
}


\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm,itemsep=-2.5mm]}

\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex,noitemsep,labelsep=0mm,itemsep=.2mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-0.8mm}}

\renewcommand{\arraystretch}{1}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------



%-------------------------------------------

\begin{document}
\fontfamily{cmr}\selectfont

%----------HEADING-----------------
\begin{center}
    \LARGE{\textbf{Katie Ng}}
\end{center}
\vspace{-6.5mm}
\begin{center}{ngkatie16@gmail.com | (718) 688-9177}
\end{center}
\vspace{-3mm}

%-----------EDUCATION-----------------

\vspace{-2.5mm}
\section{Education}

\resumeSubHeadingListStart
\resumeExp
{Stevens Institute of Technology} 
{Bachelor of Science in Computer Science, Minor in Quantitative Finance (GPA: 3.53/4.00)}
{Hoboken, NJ}
{Aug 2021 - May 2025}
\resumeItemListStart
\item[\tiny$\bullet$] Relevant Coursework: Data Structures and Algorithms, Discrete Structures, Probability and Statistics
\item[\tiny$\bullet$] Activities: Pinnacle Research, Women in Computer Science, Society of Women Engineers (SWE), Alpha Phi
\item[\tiny$\bullet$] Honors: Dean's List, Pinnacle Scholar, Presidential Scholar, Edwin A. Stevens Scholar, Martha Bayard Scholar
\resumeItemListEnd

\resumeExp
{Stuyvesant High School} 
{Specialized High School Regents Diploma with Advanced Designation (GPA: 94/100)}
{New York, NY}
{Sep 2017 - Jun 2021}

\resumeSubHeadingListEnd

%----------TECHNICAL SKILLS----------------

\section{Technical Skills}
\vspace{0.2mm}

\small{\begin{tabular*}{\textwidth}[t]{p{0.5\textwidth} p{0.5\textwidth}}

\hspace{-2.1mm}{\textbf{Languages:} Python, C++, Java, Racket, NetLogo, Arduino} & {\textbf{Web Technologies:} HTML, CSS, JavaScript} \\  
\hspace{-3.1mm}{\textbf{ Tools:} Pandas, Matplotlib, Git, Latex, Visual Studio Code}
\end{tabular*}}
\vspace{-4mm}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeExp
{Extended Reality (XR) Laboratory}
{Lab Support Specialist}
{Hoboken, NJ}
{Sep 2022 - Present}
\vspace{1mm}
\resumeItemListStart
\item[\tiny$\bullet$] Researched applications and current developments in virtual and mixed reality to assist professors in incorporating XR and 3D computer modeling into coursework for a more immersive learning experience.
\item[\tiny$\bullet$] Managed modules allowing students to develop predictive models for antibody stability, to "physically" edit genes using CRISPR-Cas9, and to test mechanical prototypes in virtual spaces.
\item[\tiny$\bullet$] Trained faculty and students to handle XR technologies and systems, including the HoloLens 2, HTC Vive, HTC Vive Pro, and Meta Oculus Quest. 
\resumeItemListEnd

\resumeExp
{Mobile AI Cybersecurity Computing (MACC) Laboratory}
{Undergraduate Researcher}
{Hoboken, NJ}
{May 2022 - Present}
\vspace{1mm}
\resumeItemListStart
\item[\tiny$\bullet$] Investigated the effect of resource selection window length on the reliability of cellular vehicle-to-everything.
\item[\tiny$\bullet$] Evaluated the feasibility of autonomous resource selection in high-density traffic. Validated its advantage over dedicated short-range communications in regard to latency and Packet Reception Ratio.
\item[\tiny$\bullet$] Developed simulations in Eclipse SUMO, manipulated object behavior through the Traffic Control Interface (TraCI) in Python, and applied vehicular communications in ns-3. Visualized data with pandas.
\resumeItemListEnd

\resumeExp
{The Stuyvesant Indicator}
{Editor-in-Chief}
{New York, NY}
{Nov 2019 - June 2021}
\vspace{1mm}
\resumeItemListStart
\item[\tiny$\bullet$] Constructed project timelines and monitored workflow for 8 departments of 240 staff members.
\item[\tiny$\bullet$] Edited all journalistic elements and graphic design in Adobe InDesign for 320-page publication.
\item[\tiny$\bullet$] Led business campaigns to fundraise \$14,500. Allocated budget for production costs.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5mm}

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeProject
{Digital Home Assistant}
{Aug 2022}
\vspace{0mm}
\resumeItemListStart
\item[\tiny$\bullet$] Built a home assistant powered by Raspberry Pi to display upcoming calendar events and real-time news.
\item[\tiny$\bullet$] Integrated Canvas and Amazon Alexa modules to display course assignments and to enable voice control.
\item[\tiny$\bullet$] Styled user interface with CSS to color-code events and deadlines by category.
\resumeItemListEnd

\resumeProject
{Music Recommendation System}
{Apr 2022}
\vspace{0mm}
\resumeItemListStart
\item[\tiny$\bullet$] Streamlined workflow for a team of 3 to develop a Python script that suggest new music artists based on users' previously liked artists.
\item[\tiny$\bullet$] Outlined sprint goals based on deadline and delegated tasks amongst team members.
\item[\tiny$\bullet$] Implemented modular programming to optimize collaborative code. Wrote 6 test cases to ensure code quality.
\resumeItemListEnd

\resumeProject
{Weather Monitoring Station}
{Dec 2021}
\vspace{0mm}
\resumeItemListStart
\item[\tiny$\bullet$] Directed a team of 3 through a product development process to design and assemble a self-contained circuit (using a WeMos board, DHT sensor, and photocell) that monitors temperature, humidity, and light intensity.
\item[\tiny$\bullet$] Implemented automatic low power mode and data validation in Arduino to optimize battery life and to minimize measurement errors. Uploaded readings through a publisher-subscriber model using MQTT protocols in IoT.
\item[\tiny$\bullet$] Designed several hardware prototypes in SolidWorks and assessed their readiness for production based on metrics such as serviceability, print time, functionality, and consumer safety.
\resumeItemListEnd

\resumeProject
{HIV Transmission and Prevention Model}
{Jan 2019}
\vspace{0mm}
\resumeItemListStart
\item[\tiny$\bullet$] Programmed a NetLogo simulation allowing users to observe dependencies between consistent prevention practices, HIV infections, and the onset of AIDS.
\item[\tiny$\bullet$] Researched transmission rates, risk factors, and infection timelines to provide an accurate real-world model.
\item[\tiny$\bullet$] Maintained thorough documentation of project versions as bugs were fixed and new features were implemented.

\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

