%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeExp
{Johnson \& Johnson}
{Technology Intern}
{}
{May 2023 - Present}
\vspace{1mm}
\resumeItemListStart
\item[\tiny$\bullet$] \textbf{Maintained a product backlog and participated in weekly standups for 15+ global stakeholders} to translate business needs into technical sprints, ensuring timely deployment for consolidation of 7 supply chain ERPs.
\item [\tiny$\bullet$] \textbf{Assisted in UI/UX development for business report dashboards} enabling a medical disposal and returns program across several countries.
\item [\tiny$\bullet$] \textbf{Created visual explanations to illustrate technical dependencies between two programs}, allowing the team to address gaps to drive customer-centric design.
\resumeItemListEnd

\resumeExp
{Extended Reality (XR) Laboratory}
{Lab Support Specialist}
{}
{Sep 2022 - May 2023}
\vspace{1mm}
\resumeItemListStart
\item[\tiny$\bullet$] \textbf{Managed modules supporting 5 university classes and 6 research teams} in gene editing, mechanical prototyping, and developing predictive models for drug stability.
\item[\tiny$\bullet$] \textbf{Trained 220+ students and 15+ faculty members} to handle 9 XR systems, including Microsoft HoloLens 2, HTC Vive Pro, and Meta Oculus Rift.
\item[\tiny$\bullet$] \textbf{Researched new developments in the metaverse} to identify innovative technologies and educational strategy.
\resumeItemListEnd

\resumeExp
{Mobile AI Cybersecurity Computing (MACC) Laboratory}
{Undergraduate Researcher}
{}
{May 2022 - Aug 2022}
\vspace{1mm}
\resumeItemListStart
\item[\tiny$\bullet$] \textbf{Leveraged pandas to identify an optimal resource selection window} ensuring 98\% success for message delivery in cellular vehicle-to-everything (CV2X) communications.
\item[\tiny$\bullet$] \textbf{Analyzed the performance of WiFi-based DSRC versus 4G/5G CV2X}, concluding that DSRC outperformed by 97\% in latency, but CV2X was 117\% more reliable with packet reception.
\item[\tiny$\bullet$] \textbf{Developed traffic simulations and modeled vehicular networks} in Eclipse SUMO and ns-3.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-7mm}